\documentclass[11pt, a4paper]{article} 

\usepackage[T1]{fontenc}     % We are using pdfLaTeX,
\usepackage[utf8]{inputenc}  % hence this preparation
\usepackage[british]{babel}  
\usepackage[left = 0mm, right = 0mm, top = 0mm, bottom = 0mm]{geometry}
\usepackage[stretch = 25, shrink = 25, tracking=true, letterspace=30]{microtype}  
\usepackage{graphicx}        % To insert pictures
\usepackage{xcolor}          % To add colour to the document
\usepackage{marvosym}        % Provides icons for the contact details

\usepackage{enumitem}        % To redefine spacing in lists
\setlist{parsep = 0pt, topsep = 0pt, partopsep = 1pt, itemsep = 1pt, leftmargin = 6mm}

\usepackage{FiraSans}        % Change this to use any font, but keep it simple
\renewcommand{\familydefault}{\sfdefault}

\definecolor{cvblue}{HTML}{304263}

%%%%%%% USER COMMAND DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%
% These are the real workhorses of this template
\newcommand{\dates}[1]{\hfill\mbox{\textbf{#1}}} % Bold stuff that doesn’t got broken into lines
\newcommand{\is}{\par\vskip.5ex plus .4ex} % Item spacing
\newcommand{\smaller}[1]{{\small$\diamond$\ #1}}
\newcommand{\headleft}[1]{\vspace*{3ex}\textsc{\textbf{#1}}\par%
    \vspace*{-1.5ex}\hrulefill\par\vspace*{0.7ex}}
\newcommand{\headright}[1]{\vspace*{2.5ex}\textsc{\Large\color{cvblue}#1}\par%
     \vspace*{-2ex}{\color{cvblue}\hrulefill}\par}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[colorlinks = true, urlcolor = white, linkcolor = white]{hyperref}

\begin{document}

% Style definitions -- killing the unnecessary space and adding the skips explicitly
\setlength{\topskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\fboxsep}{0pt}
\pagestyle{empty}
\raggedbottom

\begin{minipage}[t]{0.33\textwidth} %% Left column -- outer definition
%  Left column -- top dark rectangle
\colorbox{cvblue}{\begin{minipage}[t][5mm][t]{\textwidth}\null\hfill\null\end{minipage}}

\vspace{-.2ex} % Eliminates the small gap
\colorbox{cvblue!90}{\color{white}  %% LEFT BOX
\kern0.09\textwidth\relax% Left margin provided explicitly
\begin{minipage}[t][293mm][t]{0.82\textwidth}
\raggedright
\vspace*{2.5ex}

\Large Ali \textbf{\textsc{Arfa}} \normalsize 

\vspace*{0.5ex} % Extra space after the picture

\headleft{Profile Summary}
Passionate and detail-oriented \textit{Data Scientist} and \textit{Research Assistant} with extensive experience in programming, data analysis, web development, and machine learning. Proven track record in leading cross-functional teams, developing backend solutions, and enhancing user interfaces. Adept at utilizing advanced tools and methodologies to deliver insightful data-driven solutions. Strong communicator with a keen ability to translate complex data into actionable insights.

\headleft{Contact details}
\small % To fit more content
\MVAt\ {\small aliarfa852@gmail.com} \\[0.4ex]
\Mobilefone\ +92\,322\,7141420 \\[0.5ex]
\Letter\ Islamabad, Pakistan\\
\hyperlink{www.linkedin.com/in/aliarfa852}{linkedin aliarfa852}\\
\hyperlink{https://github.com/AliArfa852}{Git AliArfa852}


\normalsize

\headleft{Skills}
\begin{itemize}
\item \textbf{Programming Languages:} Python, C++, C , C# , JavaScript, Visual Basic, NODE.JS
\item \textbf{Database Management:} MongoDB, MySQL
\item \textbf{Web Development:} HTML \& CSS, React
\item \textbf{Tools:} Figma, GPT, Hugging Face, Hadoop, Spark, Kafka, micro python, React, Express, Rag
\item \textbf{Data Analysis:} Big Data Analysis, Data Visualization, D3
\item \textbf{AI,NLP, Edge Computation and Machine Learning}
\end{itemize} 

\end{minipage}%
\kern0.09\textwidth\relax%%Right margin provided explicitly to stretch the colourbox
}
\end{minipage}% Right column
\hskip2.5em% Left margin for the white area
\begin{minipage}[t]{0.56\textwidth}
\setlength{\parskip}{0.8ex}% Adds spaces between paragraphs; use \\ to add new lines without this space. Shrink this amount to fit more data vertically

\vspace{2ex}

\headright{Experience}

\textsc{Research Assistant} at \textit{KDD Lab, Islamabad}  \dates{April 2024--Present} \\
\smaller{Project Lead for three teams: Image Diffusion, Visualization Chatbot, and Git Crawler.} \\
\smaller{Managed and coordinated the development of innovative solutions in AI and data science.}
\smaller{Worked on edge technology, integrating SLM on edge devices and controlling hardware.} \\
\is
\textsc{Intern} at \textit{KDD Lab, Islamabad}  \dates{March 2023--April 2024} \\
\smaller{worked on NCAI project as a group lead during the summer internship.} \\
\smaller{Led a cross-functional team to implement new features and enhance the web interface.} \\
\smaller{Successfully led the team in delivering audio and video analysis for live interviews as well as improving the frontend.}
\smaller{Spearheaded backend development for seamless integration of functionalities.} \\
\smaller{Worked on LLMs and language models.} \\


\is
\textsc{Instructor} at \textit{Adastra Academy, Lahore}  \dates{June 2018--June 2018} \\
\smaller{Designed and conducted workshops on building Arduino-based robots.} \\
\smaller{Instructed participants on hardware assembly and code functionality.} \\
\smaller{Demonstrated troubleshooting techniques and provided one-on-one assistance for project success.}

\headright{Education}





\textsc{FAST NUCES, Islamabad} \\
\smaller{BSDS} \dates{August 2021--Present}
\is
\textsc{The City School DHA, Lahore} \\
\smaller{A' Level} \dates{August 2019--June 2021}
\is
\textsc{The City School DHA, Lahore} \\
\smaller{O' Level} \dates{August 2016--June 2019}

\headright{Personal Projects}

\smaller{\textsc{Age and Gender Prediction}} \\

\is
\smaller{\textsc{ESP WiFi-Based Toy Car Controls}} \\
\is
\smaller{\textsc{Hand Gesture Controlled Bot }} \\
\is
\smaller{\textsc{RAG PDF Chatbot}} \\

\headright{Hobbies}

\textit{Listening to Music, Making Bots, Driving}

\end{minipage}

\end{document}
